When are Fuzzy Extractors Possible?

### 2015-01-30 trunk/info-bounds/FuzzyExtPossibility.tex
incerted some notes

There exists a set $R_{small}$  where $|R_{small} | \ge 2^{\kappa-1}$ such that for all $\key\in R_{small}$,  $|Q_{p^*, r}|\le \mathcal{M}/2^{\kappa} = 2^{n-\kappa }$.  If not, then $\cup_{\key} |Q_{p^*, \key}| > |\mathcal{M}|$.
For the remainder of the proof we restrict ourselves to elements in $R_{small}$.  Only points that are distance $t$ from points outside of $Q_{p^*, r}$ are viable points in the metric space.  These are the interior of $Q_{p^*, r}$:
\begin{align*}
\inter(Q_{p^*, \key}) = \{w | \rep(w, p^*) = \key \wedge \forall w', \dis(w, w') \le t \wedge \rep(w', p^*) =\key\},\\
%\crust(Q_{p^*, r}) = \{w | \rep(w, p^*) = r \wedge \exists w', \dis(w, w')\le t \wedge \rep(w', p^*) \neq r\}.
\end{align*}

%Note that $\crust(Q_{p^*, r}) \cap \inter(Q_{p^*,r}) =\emptyset$.  
We will use the term deficient ball\footnote{In most statements of the isoperimetric inequality, this type of set is simply called a ball.  We use the term deficient ball for emphasis.}:\bnote{use a term other than deficient}
\begin{definition}
A set $S$ is a $\eta$-deficient ball if there exists a point $x$ such that $B_{\eta-1}(x) \subseteq S \subseteq B_{\eta}(x)$.
\end{definition}

@@

\begin{lemma}
$|\inter(Q_{p^*, \key^*})| \le 2^{n-4\nu}$.
\end{lemma}
\begin{proof}
By the isoperimetric inequality on the Hamming space~(we use a version
due to~\cite[Theorem 1]{frankl1981short}, the original result is due
to Harper~\cite{harper1966optimal}), there exists a $\eta$-deficient
ball $S_{p^*, \key^*}$ centered at $0^n$ and a deficient ball $D$,
centered at $1^n$, such that
$|S_{p^*, \key^*}| = |\inter(Q_{p^*, \key^*})|$, $|D| = |Q_{p^*,
  \key^*}^\complement|$ (where $\cdot^\complement$ denotes the
complement of a set) and $\forall s\in S_{p^*, \key^*}, d\in D$,
$\dis(s, d) \ge t$~(that is, the distance between the sets is $t$).  Note that $S_{p^*, \key^*} \cup D^\complement$ is a deficient ball~(and its radius is $\eta+t$).
We now bound the size of $S_{p^*, \key^*}$.

Recall that $|S_{p^*, \key^*} \cup D| = |Q_{p^*, \key^*} | \le 2^{n-\kappa}\leq |\mathcal{M}|/2$.  Since this set contains less than half the points in the metric space we know its radius at most $n/2$.  This means that $|S_{p^*, \key^*}|$ is a deficient sphere of radius at most $n/2-t$.  Let $X$ denote a uniform string on $\zo^n$.  We use Hoeffding's inequality~\cite{hoeffding1963probability}:

>>>>

There exists a set $R_{small}$  where $|R_{small} | \ge 2^{\kappa-1}$ such that for all $\key\in R_{small}$,  $|Q_{p^*, r}|\le \mathcal{M}/2^{\kappa} = 2^{n-\kappa }$.  If not, then $\cup_{\key} |Q_{p^*, \key}| > |\mathcal{M}|$.
For the remainder of the proof we restrict ourselves to elements in $R_{small}$.  Only points that are distance $t$ from points outside of $Q_{p^*, r}$ are viable points in the metric space.  These are the interior of $Q_{p^*, r}$: \lnote{what's $r$? in this and previous lines? also, I can parse definition of interior below}
\begin{align*}
\inter(Q_{p^*, \key}) = \{w | \rep(w, p^*) = \key \wedge \forall w', \dis(w, w') \le t \wedge \rep(w', p^*) =\key\},\\
%\crust(Q_{p^*, r}) = \{w | \rep(w, p^*) = r \wedge \exists w', \dis(w, w')\le t \wedge \rep(w', p^*) \neq r\}.
\end{align*}

%Note that $\crust(Q_{p^*, r}) \cap \inter(Q_{p^*,r}) =\emptyset$.  
We will use the term deficient ball\footnote{In most statements of the isoperimetric inequality, this type of set is simply called a ball.  We use the term deficient ball for emphasis.}:\bnote{use a term other than deficient} \lnote{how about ``almost ball''}
\begin{definition}
A set $S$ is a $\eta$-deficient ball if there exists a point $x$ such that $B_{\eta-1}(x) \subseteq S \subseteq B_{\eta}(x)$.
\end{definition}

@@

\begin{lemma}
$|\inter(Q_{p^*, \key^*})| \le 2^{n-4\nu}$.
\end{lemma}
\begin{proof}
By the isoperimetric inequality on the Hamming space~(we use a version
due to~\cite[Theorem 1]{frankl1981short}, the original result is due
to Harper~\cite{harper1966optimal}), there exists a $\eta$-deficient
ball $S_{p^*, \key^*}$ centered at $0^n$ and a deficient ball $D$,
centered at $1^n$, such that
$|S_{p^*, \key^*}| = |\inter(Q_{p^*, \key^*})|$, $|D| = |Q_{p^*,
  \key^*}^\complement|$ (where $\cdot^\complement$ denotes the
complement of a set) and $\forall s\in S_{p^*, \key^*}, d\in D$,
$\dis(s, d) \ge t$~(that is, the distance between the sets is $t$).  Note that $S_{p^*, \key^*} \cup D^\complement$ is a deficient ball~(and its radius is $\eta+t$).\lnote{Why?}
We now bound the size of $S_{p^*, \key^*}$.

Recall that $|S_{p^*, \key^*} \cup D| = |Q_{p^*, \key^*} | \le 2^{n-\kappa}\leq |\mathcal{M}|/2$.  Since this set contains less than half the points in the metric space we know its radius at most $n/2$.  This means that $|S_{p^*, \key^*}|$ is a deficient sphere \lnote{ball} of radius at most $n/2-t$.  Let $X$ denote a uniform string on $\zo^n$.  We use Hoeffding's inequality~\cite{hoeffding1963probability}: \lnote{should the first $n$ in the line below be $n/2$?}
